\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}

\begin{document}
	\title{Stroke Background}
	\date{}
	\maketitle
	\section{Background}
	\subsection{Stoke and Breathing Patterns}
	Anomalous breathing patterns are often found in stroke patients during sleep. A. Ferrea et al.\cite{ferre2013strokes} investigated studies performed during the acute phase of stroke and stated that 59\% patients frequently present breathing changes. Bonnin-Vilaplana et al.\cite{bonnin2009sleep} found that 69\% of acute lacunar stroke patients present breathing changes. Stroke can also cause many breathing complications, such as periodic breathing, central neurogenic yyperventilation, apneustic breathing, ataxic breathing and so on\cite{rochester2002respiratory}.
	
	
	
	
	
	
	\subsection{Stroke and Asymmetric Movement}
	Patients will present movement disorders after stroke, one of them is movement asymmetry. Patterson KK et al.\cite{patterson2008gait} found that 55.5\% participants showed significant temporal temporal gait asymmetry and 33.3\% exhibited statistically significant spatial asymmetry. Hodt-Billington et al.\cite{hodt2008should} found that trunk movement of stroke patients is also asymmetry. Neha Lodha et al.\cite{lodha2012bimanual} found the increased asymmetry in force produced by hand in stroke group.
	
	
	\subsection{Stroke and Sleeping Position}
	
	Millene R. Camilo et al.\cite{camilo2012supine} and Devin L. Brown rt al.\cite{brown2008high} both stated that supine positioning during sleep is highly frequent after stroke, which is related to sleep apnea.
	
	
	\bibliography{bibtex}{}
	\bibliographystyle{plain}
\end{document}